### 2018-03-28 latex/sc18/prelims.tex
Prelims
MPI collectives to prelims

	Tensors will be denoted using Euler script (e.g., $\T{T}$), matrices will be denoted (e.g., $\M{M}$), vectors will be denoted as lower case bold face type (e.g., $\V{v}$), and scalars will not be bolded (e.g., $s$). Matlab style notation will be sued to index into tensors, matrices, and vectors. For example, $\M{M}(:,c)$ gives the cth column of the matrix M.
	The Hadamard product is the element wise matrix product and will be denoted using $*$. 
	The Khatri-Rao product, abbreviated KRP, will be denoted with $\Khat$. Given matrices $\M{A}$ and $\M{B}$ that are $I_{A} \times R$ and $I_{B} \times R$, the KRP $\M{K} = \M{A} \Khat \M{B}$ is $I_{A}I_{B} \times R$. It can be thought of as a series row-wise Hadamard products s.t. \\$\M{K}(0:) = \M{A}(0,:) * \M{B}(0,:)\\ \M{K}(1:) = \M{A}(0,:) * \M{B}(1,:)  \\.\\.\\. \\ \M{K}(I_{A}I_{B} - 1,:) = \M{A}(I_{A}-1,:) * \M{B}(I_{B}-1,:)$

>>>>

Tensors will be denoted using Euler script (e.g., $\T{T}$), 
matrices will be denoted (e.g., $\M{M}$), vectors will be denoted as lower case bold face type 
(e.g., $\V{v}$), and scalars will not be bolded (e.g., $s$). 
Matlab style notation will be sued to index into tensors, matrices, and vectors. 
For example, $\M{M}(:,c)$ gives the cth column of the matrix M.
The Hadamard product is the element wise matrix product and will be denoted using $*$. 
The Khatri-Rao product, abbreviated KRP, will be denoted with $\Khat$. 
Given matrices $\M{A}$ and $\M{B}$ that are $I_{A} \times R$ and $I_{B} \times R$, the KRP $\M{K} = \M{A} \Khat \M{B}$ is $I_{A}I_{B} \times R$. 
It can be thought of as a series row-wise Hadamard products s.t.
 \\$\M{K}(0:) = \M{A}(0,:) * \M{B}(0,:)\\ \M{K}(1:) = \M{A}(0,:) * \M{B}(1,:)  \\.\\.\\. \\ \M{K}(I_{A}I_{B} - 1,:) = \M{A}(I_{A}-1,:) * \M{B}(I_{B}-1,:)$ \\
 The Matricized Tensor Times Khatri Rao Product or MTTKRP will be central to this work and takes the form $\M{M} = \M{X}_{(n)}( \Mn{H}{N-1} \Khat \cdots \Khat \Mn{H}{n-1} \Khat \Mn{H}{n+1} \Khat  \cdots \Khat \Mn{H}{0})$. $\M{X}_{(n)}$ is a matrix formed by taking the nth mode fibers of a tensor $\T{X}$ with dimensions $I_{0} \times I_{1} \times ... \times I_{N-1}$ and making them the columns of a matrix.

%MPI collectives for Prelims
To implement and analyze our algorithms we use the MPI collective communication model of distributed-memory parallel computation. Setting $W$ to be the number of words in a message between two processors, $\alpha$ to be the latency, and $\beta$ to be the per word cost, the total cost of a message is $\alpha + \beta W$. Reduce operations also include a flop cost but we will ignore it both for simplicity and the fact that cost is often dominated by communication. For a more in-depth discussion of the MPI model and its efficient collectives see [NEED CITATION],[NEED CITATION]. The collectives utilized in this work and their costs are the 
\begin{itemize}
\item All Reduce $2\alpha log P + 2\beta W (P-1)/P$
\item All Gather $\alpha log P + \beta W (P-1)/P$
\item Reduce Scatter $\alpha log P + \beta W (P-1)/P$
\end{itemize}
